### 2024-03-16 content/chapter_1.tex
:pencil: Add applications

	Before delving into these questions, we first provide a short overview of \gls{ris} and introduce some potential applications in the next section.
	A detailed literature review and technical discussion on \gls{ris} and other topics will be reserved for Chapter \ref{ch:background}.
\end{section}

\begin{section}{Overview on \glsfmtfull{ris}}
	% and may be evolved into a versatile tool, which blurs the boundary between the network and environment.
	% This vision motivates us to explore the fundamental limits of \gls{ris} and integrate it with state-of-the-art wireless technologies.

@@

	\begin{subsection}{Concept}
		\gls{ris} is commonly known as a planar surface involving numerous wave scattering elements (a.k.a. unit cells, reflective patches), whose amplitude and phase responses can be engineered in real-time to achieve a desired radiation pattern.
		As shown in Fig. \ref{fg:ris_architecture}, its typical architecture consists of three stacked layers and a controller \cite{Wu2020}.
		The top layer is a two-dimensional array of scattering elements printed on a dielectric substrate.
		The elements directly interact with the impinging waves, which are usually fabricated from metamaterial or patch/dipole antennas with sub-wavelength dimension and spacing.
		The middle layer is a copper ground plate that provides voltage reference and avoids signal leakage.
		The bottom later is a circuit board that associate each element with adjustable components like varactor and \gls{pin} diodes \cite{Dai2020}.
		It also hosts a \gls{fpga} controller that controls the circuit and coordinate with other devices in the network.
		By adjusting the scatter response of each element, the \gls{ris} can effectively manipulate the wavefront and thus improve the ambient wireless environment.
		\begin{figure}
			\centering
			\includegraphics[width=0.9\textwidth]{ris_architecture.pdf}
			\caption{A typical architecture of \gls{ris} \cite{Wu2020}.}
			\label{fg:ris_architecture}
		\end{figure}
	\end{subsection}

	\begin{subsection}{Characteristics}
		The key characteristics of \gls{ris} are summarized as follows:
		\begin{itemize}
			\item \emph{Passive and environmental-friendly:} \gls{ris} reflects the incident waves in a passive manner and does not require dedicated \gls{rf} chains.\footnote{The controller may be implemented with low-power components and powered by ambient energy.} This is different from \gls{af} relays that require power-hungry oscillators and introduces additional thermal noise.
			\item \emph{Flexible:} It provides a software configurable environment that can be adapted for different applications and scenarios. This is different from reflectarray \cite{Nayeri2018} and frequency selective surfaces \cite{Anwar2018} with predefined radiation patterns and frequency response.
			\item \emph{Full-duplex and universal:} This physical-layer solution can simultaneously benefit downlink and uplink thanks to channel reciprocity \cite{Wu2021}, and simultaneously support communication, sensing, and power transfer without self-interference. This is different from \gls{df} relays that are designed for a specific communication link and suffers from packet delays.
			\item \emph{Low-cost and conformal:} It can be manufactured from low-cost materials and deployed in various forms (e.g., walls, windows, ceilings, tables) to provide seamless coverage and powerful customization for indoor and outdoor environments. This is different from conventional multi-antenna systems that features complex hardware and bulky structures.
		\end{itemize}
	\end{subsection}

	\begin{subsection}{Applications}

	% This disruptive technology can be introduced to legacy networks for signal enhancement, interference suppression, scattering enrichment, blockage bypassing, coverage extension, and security control.
	\end{subsection}
\end{section}

@@

		\item Chapter \ref{ch:introduction} introduces \gls{ris} as a promising technology for ambient wave redirection and highlights its potential benefits in future wireless networks. It discusses the motivation, objectives, and contributions of each research chapter. A list of publications is also provided.
		\item Chapter \ref{ch:background} provides the necessary background knowledge for the subsequent chapters, including the fundamental concepts, operating principles, hardware implementation, signal and system models, performance metrics, and design challenges for \gls{ris}, \gls{wpt}, \gls{swipt}, \gls{bc}, and \gls{mimo} systems. It also reviews the state-of-the-art research in relevant topics and raise critical questions to be addressed in the following chapters.

>>>>

	Before delving into these questions, we first provide a short overview of \gls{ris} and introduce some potential applications.
	A detailed literature review and technical discussion on \gls{ris} and other topics will be reserved for Chapter \ref{ch:background}.
\end{section}

\begin{section}{Overview on \glsfmtfull{ris}}

	% and may be evolved into a versatile tool, which blurs the boundary between the network and environment.
	% This vision motivates us to explore the fundamental limits of \gls{ris} and integrate it with state-of-the-art wireless technologies.

@@

	\begin{subsection}{Concept}
		\gls{ris} is commonly known as a planar surface involving numerous wave scattering elements (a.k.a. unit cells, reflective patches), whose amplitude and phase responses can be engineered in real-time to achieve a desired radiation pattern.
		As shown in Fig. \ref{fg:ris_architecture}, its typical architecture consists of three stacked layers and a controller \cite{Wu2020}.
		The top layer is a two-dimensional array of scattering elements printed on a dielectric substrate.
		The elements directly interact with the impinging waves, which are usually fabricated from metamaterial or patch/dipole antennas with sub-wavelength dimension and spacing.
		The middle layer is a copper ground plate that provides voltage reference and avoids signal leakage.
		The bottom later is a circuit board that associate each element with adjustable components, such as varactor and \gls{pin} diodes \cite{Dai2020}.
		It also hosts a \gls{fpga} controller that controls the circuit and coordinate with transceivers in the network.
		By adjusting the scatter response of all elements, the \gls{ris} can effectively manipulate the wavefront for a constructive or destructive superposition and thus improve the ambient wireless environment.
		\begin{figure}
			\centering
			\includegraphics[width=0.9\textwidth]{ris_architecture.pdf}
			\caption{A typical architecture of \gls{ris}. Modified from \cite{Wu2020}.}
			\label{fg:ris_architecture}
		\end{figure}
	\end{subsection}

	\begin{subsection}{Characteristics}
		The key characteristics of \gls{ris} are summarized as follows:
		\begin{itemize}
			\item \emph{Passive and environmental-friendly:} \gls{ris} reflects the incident waves in a passive manner and does not require dedicated \gls{rf} chains.\footnote{The controller may be implemented with low-power components and powered by ambient energy.} This is different from \gls{af} relays that require power-hungry oscillators and introduces additional thermal noise.
			\item \emph{Flexible:} It provides a software configurable environment that can be adapted for different applications and scenarios. This is different from conventional reflectarray \cite{Nayeri2018} and frequency selective surfaces \cite{Anwar2018} with predefined radiation patterns and frequency response.
			\item \emph{Full-duplex and universal:} This physical-layer solution can simultaneously support communication, sensing, and power transfer without self-interference. Thanks to channel reciprocity, the optimal configuration for downlink and uplink coincide with each other \cite{Wu2021}. This is different from \gls{df} relays that are designed for a specific communication link and suffers from packet delays.
			\item \emph{Low-cost and conformal:} It can be manufactured from low-cost materials and deployed in various forms (e.g., walls, windows, ceilings, tables) to provide seamless coverage and powerful customization for indoor and outdoor environments. This is different from conventional multi-antenna systems that features complex hardware and bulky structures.
		\end{itemize}
	\end{subsection}

	\begin{subsection}{Applications}
		The channel manipulation capability of \gls{ris} unlocks a wide range of unprecedented applications, such as signal enhancement \cite{Wu2019}, interference suppression \cite{Jiang2022}, blockage bypassing \cite{Ghatak2021}, coverage extension \cite{Zeng2021}, and security control \cite{Almohamad2020}.
		It also has the potential to convey additional information \cite{Ye2022}, compensate for the Doppler effect \cite{Basar2021}, transform frequency-selective channels into frequency-flat \cite{Arslan2022}, improve the spatial diversity for multi-antenna systems \cite{Ozdogan2020a}, and create artificial time diversity for multi-user orthogonal \cite{Yang2019} and non-orthogonal \cite{Chen2023} multiple accesses.

		Those fancy characteristics and applications of \gls{ris} have also attracted significant attention from the industry.
		The first public testing attempt was made in 2018 by NTT Docomo and Metawave, which demonstrated a metasurface reflectarray in the FR2 band of 5G can boost a downlink data rate from \qty{60}{Mbps} to \qty{560}{Mbps} \cite{Liu2022b}.
		Later in 2020, NTT Docomo developed a transparent dynamic \gls{ris} that can allows 28GHz signals to reflect or pass through with negligible power loss.
		A regional ``\gls{ris} alliance'' was formed in 2021 by Chinese companies and institutes including ZTE, China Mobile, and CAICT, which soon released a white paper \cite{Rista2023} to promote the technology and standardization.
		In December 2022, ITU-R drafted a recommendation report for IMT-2030 (6G) \cite{Itu2022} that marks \gls{ris} as a key technology to enhance the radio interface for multiple physical dimension transmission.
		These developments showcase the rapid progress of \gls{ris} from theoretical concept to practical implementation, paving the way for its integration into the next-generation network.
	\end{subsection}
\end{section}

@@

		\item Chapter \ref{ch:introduction} provides an overview of the thesis. It introduces the background and motivation, discusses the characteristics and applications of \gls{ris}, and summarizes the objectives and contributions of each research chapter. A list of publications is also provided.
		\item Chapter \ref{ch:background} provides the necessary background knowledge for the subsequent chapters, including the fundamental principles, hardware implementation, signal and system models, performance metrics, and design challenges for \gls{ris}, \gls{wpt}, \gls{swipt}, \gls{bc}, and \gls{mimo} systems. It also reviews the state-of-the-art research in relevant topics and raise critical questions to be addressed in the following chapters.
